Response to Reviewers - Article 4780

### 2024-01-04 cubble.Rmd
review response and revision changes made

The Bureau of Meteorology collects water level data that can be matched with precipitation data from climate weather stations. The data \code{river} from the \pkg{cubble} package contains water course level data for 71 river gauges collected in Victoria, Australia. Victoria weather station data can be subsetted from the \code{climate_aus} data in the \pkg{cubble} package. This example demonstrates the use of the matching function introduced in Section \ref{matching} to find river gauges that mirror changes in precipitation regimes captured in the climate weather stations in Victoria.

@@

Ideal matches would exhibit a spatial proximity and also a temporal similarity, with a potential offset due to translating the rainfall into water level. This motivates the two step approach where a spatial match on the site locations is first performed between both data sets. The rainfall recorded at a particular station can directly impact the water level in nearby rivers, which emphasizes the need to find related or matching locations. With \code{match_spatial()}, we can obtain a summary of the 10 closest pairs of weather stations and river gauges:

@@

The results can also be returned as a list of matched cubbles, by setting the argument \code{return_cubble = TRUE}. After excluding the two pairs where a river station is matched to more than one weather stations (river station 226027 is matched twice in group 3 and 5 and similarly for station 230200 in group 7 and 8), all the results can be combined into a single cubble using \code{bind_rows()},

@@

@@

Possible future directions would be in two main directions: handling much larger data sets, and integrating smoothly with modeling. Spatio-temporal data can be huge, and the current recommendation is to first reduce the spatial and temporal components before constructing a cubble. Better support could be provided with additional pre-processing functions. Considerable effort has been exerted to provide tidy tools for models, with the \pkg{tidymodels} project. It provides the infrastructural interface to build vast array of statistical and machine learning models. A similar direction would be to extend cubble to provide a more unified interface to spatio-temporal modeling.

>>>>

This example illustrates spatio-temporal matching of water level data from stream sensors with precipitation data from climate weather stations. The data \code{river} from the \pkg{cubble} package contains water course level data for 71 river gauges collected in Victoria, Australia. Victoria weather station data can be extracted from the \code{climate_aus} data in the \pkg{cubble} package. This example demonstrates the use of the matching function introduced in Section \ref{matching} to find river gauges that mirror changes in precipitation regimes captured in the climate weather stations in Victoria.

@@

We assume that matches would be close spatially and have a similar temporal pattern, accounting for scale (volume of rainfall relative to volume of stream capacity) and temporal lags (time to take water to travel to location). This motivates a two-step approach: spatial match is first performed between both data sets, followed by a temporal pattern match on a reduced set of locations.

With \code{match_spatial()}, we can obtain a summary of the closest pairs (here it is 10) of weather stations and river gauges to print or as a list of matched cubbles (if \code{return_cubble = TRUE}). The following shows the print results:

@@

Notice from the printed list that river station 226027 matches two weather stations. This is possible, and is why printing the matching results first is preferable. The user would need to decide how to handle the multiple matches, for example by removing one or aggregating results, because a cubble requires unique IDs.  This example creates the list of matched cubbles after excluding the two pairs where a river station is matched to more than one weather station (river station 226027 is matched twice in group 3 and 5 and similarly for station 230200 in group 7 and 8). The \code{bind_rows} function is used to TODO

@@

It is possible to keep multiple matches in order to find the best temporal match among the set using the \code{spatial_n_each} argument. In combination with \code{spatial_n_group} more complicated matched pairs can be provided to the temporal matching. For example, if  \code{spatial_n_each=4} and \code{spatial_n_group=2}, two groups each with the closest four spatial neighbors would be created. The temporal matching would follow on each group.

@@

Possible future improvements would be in two main directions: handling much larger data, and integrating smoothly with modeling. Our work has been designed to make it easier to focus on intricate space-time patterns, and it expects that the analyst first reduces the data if the spatio-temporal data is huge, before creating a cubble. Additional tools for pre-processing large data would be helpful. Because the cubble structure is based on tidy data principles, it potentially integrates well with tidy tools for models, as provided by the \pkg{tidymodels} project. Although that project focuses on providing an interface to the vast array of statistical and machine learning models, it would be useful to extend its capacity to provide a more unified interface to many spatio-temporal modeling software.

### 2024-01-04 review/B-response-V2.Rmd
review response and revision changes made

### Sec. 3.1: 
  * Typo: “that can be used to match~~ed~~ the selected time series across locations. **\textcolor{purple}{Fixed.}**
  * Typo: “The function ~~on~~ calculates” **\textcolor{purple}{Fixed.}**
  * Typo: “it is possible to ~~can~~ include” **\textcolor{purple}{Fixed.}**
  * Is a matching based on index (date and time) only also possible in cubble?

@@

  * It is nice to mention the challenges of all examples, as interested users of cubble could directly jump to the relevant example for their own use case.

@@

At the very beginning of the example, please clearly motivate the two-step approach. **\textcolor{purple}{Added. The two-step approach is motivated because ideal matches require both spatial proximity and temporal similarity in trend.}** I thought I had understood it, but am again puzzled. What I understand is that you pick (i) the 10 closest pairs of met stations and river stations and then (ii) additionally require a temporal similarity (in terms of peaks). But how is the temporal offset treated and controlled in these cases? **\textcolor{purple}{see dot point 3 below}** I also see some logic in an approach where you (i) select 10 spatially closest met stations per river station (i.e. setting `spatial_n_each` = 10) and (ii) pick the highest data similarity between met and river stations within each group. Here, it might be possible, that close-by met and river stations are less related than apparently further apart stations due to local terrain and catchment boundaries. The motivation of the example is crucial and might raise awareness for unintended matches in individual user data. Please clearly describe what this example is meant to illustrate to the reader and potential user of cubble. **\textcolor{purple}{The proposed strategy to pick pairs has been considered, which motivates the arguemnt spaital\_n\_each.}**

@@

### Sec. 5:
  * “It provides a much better interface to the vast array of statistical and machine learning model architecture.” Much better than ..? **\textcolor{purple}{Changed to: It provides the infrastructural interface to build ...}**

>>>>

### Sec. 3.1: 
  * Typo: “that can be used to match~~ed~~ the selected time series across locations. **\textcolor{purple}{Fixed.}**
  * Typo: “The function ~~on~~ calculates” **\textcolor{purple}{Fixed.}**
  * Typo: “it is possible to ~~can~~ include” **\textcolor{purple}{Fixed.}**
  * Is a matching based on index (date and time) only also possible in cubble? **It can handle matching for any of the temporal objects on which cubble is based, see section 2.1. No changes made to the paper.**

@@

  * It is nice to mention the challenges of all examples, as interested users of cubble could directly jump to the relevant example for their own use case. **\textcolor{purple}{No change made, current list at top of section 4 should be sufficient for readers to jump to the example that is most relevant for them.}**

@@

At the very beginning of the example, please clearly motivate the two-step approach. I thought I had understood it, but am again puzzled. What I understand is that you pick (i) the 10 closest pairs of met stations and river stations and then (ii) additionally require a temporal similarity (in terms of peaks). But how is the temporal offset treated and controlled in these cases? I also see some logic in an approach where you (i) select 10 spatially closest met stations per river station (i.e. setting `spatial_n_each` = 10) and (ii) pick the highest data similarity between met and river stations within each group. Here, it might be possible, that close-by met and river stations are less related than apparently further apart stations due to local terrain and catchment boundaries. The motivation of the example is crucial and might raise awareness for unintended matches in individual user data. Please clearly describe what this example is meant to illustrate to the reader and potential user of cubble. **\textcolor{purple}{We have clarified the text in this section to make it clearer. Yes, you are right, that searches can accommodate a broader spatial neighborhood using the spatial\_n\_group argument, and multiple matches can be accommodated using the spatial\_n\_each argument. The revised text mentions these more complicated matching possibilities.}**

@@

### Sec. 5:
  * “It provides a much better interface to the vast array of statistical and machine learning model architecture.” Much better than ..? **\textcolor{purple}{Paragraph has been  revised, and is now much clearer.}**
